Selection figure

### 2020-05-25 main_figures/selection.Rmd
updated many figures to improve readability...
fixed latex errors

```{r, include=FALSE}
#devtools::load_all("../../pipeComp_biorxiv/pipeComp/")
```

@@

```{r}
res <- readRDS("../data/results_selection.rds")
cl <- res$clustering
vst <- cl[grep("seuratvst",row.names(cl)),]
snorm <- cl[grep("seuratvst",row.names(cl), invert=TRUE),]
h1 <- scrna_evalPlot_clustAtTrueK(snorm[grep("=1000;",row.names(snorm)),], "ARI", scale = FALSE, title="ARI at true # clusters", anno_legend = FALSE)
h2 <- scrna_evalPlot_clustAtTrueK(vst[grep("=1000;",row.names(vst)),], "ARI", scale = FALSE, reorder_rows=row.names(h1@matrix), title="sctransform\nARI at true # clusters", name="ARI2", anno_legend = FALSE)
p2 <- grid.grabExpr(draw(h1+h2))
```

>>>>

```{r, include=FALSE}
devtools::load_all("../../pipeComp_biorxiv/pipeComp/")
```

@@

```{r}
res <- readRDS("../data/results_selection.rds")
cl <- res$clustering
vst <- cl[grep("seuratvst",row.names(cl)),]
snorm <- cl[grep("seuratvst",row.names(cl), invert=TRUE),]
h1 <- scrna_evalPlot_clustAtTrueK(snorm[grep("=1000;",row.names(snorm)),], "ARI", scale = FALSE, title="ARI at true # clusters", anno_legend = FALSE, show_heatmap_legend=TRUE, heatmap_legend_param=list(direction="horizontal", at=5:10/10, title_position="leftcenter"))
h2 <- scrna_evalPlot_clustAtTrueK(vst[grep("=1000;",row.names(vst)),], "ARI", scale = FALSE, reorder_rows=row.names(h1@matrix), title="sctransform\nARI at true # clusters", name="ARI2", anno_legend = FALSE)
p2 <- grid.grabExpr(draw(h1+h2, heatmap_legend_side = "bottom", merge_legend=TRUE))
```
